\sysfull

### 2017-08-11 paper/coalescing.tex
added figure for coalescing.  need to fix text

\begin{figure}
	\centering
	\subfloat[Core of task coalescing: commit postponing]{\includegraphics[width=\columnwidth]{figures/coalescing_states}\label{fig:coalescing_example_states}}\\
	\subfloat[Adaptive task coalescing based on task failure history]{\includegraphics[width=\columnwidth]{figures/coalescing_flowchart}\label{fig:coalescing_example_flowchart}}
	\caption{\sys task coalescing process.}
	\label{fig:coalescing_example}
\end{figure}

>>>>

\begin{figure}
	\centering
	\subfloat[\sys coalesces consecutive tasks.]{\includegraphics[width=\columnwidth]{figures/coalescing_states}\label{fig:coalescing_example_states}}\\
	\subfloat[\sys dynamically adapts the amount of coalescing.]{\includegraphics[width=\columnwidth]{figures/coalescing_timeline}\label{fig:coalescing_example_flowchart}}
	\caption{\sys coalesces tasks to avoid overheads.}
	\label{fig:coalescing_example}
\end{figure}
